The Concurrent Calculi Formalisation Benchmark

### 2023-10-17 paper/paper.tex
Fix broken reference.
furhter comment about the book and paper used as sources

\section{The challenges}\label{sec:challenge-problems}
\label{sec:prelim}
First, we list some common notions and conventions that we use in the
challenges. Since the calculi under study are somewhat different, each section
lists the changes that apply. The challenges are inspired by simplified versions of calculi (and proofs) from~\cite{picalcbook} and~\cite{Vasconcelos2012}.

@@

\vspace{-1mm}%
\paragraph{Extending and combining the current challenges.}
The proposed challenges try to minimise the overlap of the techniques
and aspects they exercise (linearity, scope extrusion, coinduction) --- but most
research on concurrency theory combines some or all such aspects. A second round of formalisations could
entail combining the features of the challenges.
In \cref{table:extensions} we consider the following three extensions:
\emph{(1)} the addition of choice to the type level and the process level,
\emph{(2)} the addition of recursion (and recursive types for typed systems),
and \emph{(3)} the
addition of channel delegation to those calculi that do not already
support it.

>>>>

\section{The challenges}\label{sec:challenge-problems}
\label{sec:prelim}
First, we list some common notions and conventions that we use in the
challenges. Since the calculi under study are somewhat different, each
section lists the changes that apply. The challenges are inspired by
simplified versions of calculi (and proofs) from chapters 1 and 2
of~\cite{picalcbook} and~\cite{Vasconcelos2012} where the idea is to
use sources that can be considered standard and close to current practice.

@@

\vspace{-1mm}%
\paragraph{Extending and combining the current challenges.}
The proposed challenges try to minimise the overlap of the techniques
and aspects they exercise (linearity, scope extrusion, coinduction) --- but most
research on concurrency theory combines some or all such aspects. A second round of formalisations could
entail combining the features of the challenges.
In \cref{tab:extensions} we consider the following three extensions:
\emph{(1)} the addition of choice to the type level and the process level,
\emph{(2)} the addition of recursion (and recursive types for typed systems),
and \emph{(3)} the
addition of channel delegation to those calculi that do not already
support it.
